---
title: "labNotebook_beerEthnicityConsumptionBrandChoice"
author: "Matthew Aaron Looney"
date: "7/31/2018"
output: pdf_document
---

\newpage
  
```{r echo=F}

library(beerEthnicityConsumptionBrandChoice)

path.local <- rprojroot::find_rstudio_root_file()

```
  
```{r echo=F, cache=T, message=F, warning=F}

hora <- S4.allBrands_2010analysis( brands= c("CHICAGO", 
                                             "DALLAS, TX", 
                                             "LOS ANGELES", 
                                             "SPOKANE", 
                                             "SYRACUSE", 
                                             "HOUSTON"), 
                                    out_algoRunTime = T
                                  )

```
  
\begin{verbatim}
Algorithm name: S4.allBrands_2010analysis( brands= c("CHICAGO", 
                                                     "DALLAS, TX", 
                                                     "LOS ANGELES", 
                                                     "SPOKANE", 
                                                     "SYRACUSE", 
                                                     "HOUSTON"), 
                                            out_algoRunTime = T
                                           )  
\end{verbatim}
                            
Algorithm run time: `r difftime(hora[[2]], hora[[1]], units="min") ` minute(s).   
\newpage
  
```{r echo=F, cache=T, message=F, warning=F, fig.height=8, fig.width=9}

par(mfrow= c(1, 2), ps= 8, cex= 0.75, cex.main= 1.25)

hora <- S5.aggregate_allBrands_2010(Market = 'CHICAGO', 
                            figurePlot = T,
                            screenPlot = T,
                            saveData = T, 
                            out_algoRunTime = T)

```
  
\begin{verbatim}
Algorithm name: S5.aggregate_allBrands_2010(Market = 'CHICAGO', 
                            figurePlot = T,
                            screenPlot = T,
                            saveData = T, 
                            out_algoRunTime = T)  
\end{verbatim}
                            
Algorithm run time: `r difftime(hora[[2]], hora[[1]], units="min") ` minute(s).   
\newpage
  
```{r echo=F, cache=T, message=F, warning=F, fig.height=8, fig.width=9}

par(mfrow= c(1, 2), ps= 8, cex= 0.75, cex.main= 1.25)

hora <- S5.aggregate_allBrands_2010(Market = 'DALLAS, TX', 
                            figurePlot = T,
                            screenPlot = T,
                            saveData = T, 
                            out_algoRunTime = T)

```
  
\begin{verbatim}
Algorithm name: S5.aggregate_allBrands_2010(Market = 'DALLAS, TX', 
                            figurePlot = T,
                            screenPlot = T,
                            saveData = T, 
                            out_algoRunTime = T)  
\end{verbatim}
                            
Algorithm run time: `r difftime(hora[[2]], hora[[1]], units="min") ` minute(s).  
\newpage

```{r echo=F, cache=T, message=F, warning=F, fig.height=8, fig.width=9}

par(mfrow= c(1, 2), ps= 8, cex= 0.75, cex.main= 1.25)

hora <- S5.aggregate_allBrands_2010(Market = 'LOS ANGELES', 
                            figurePlot = T,
                            screenPlot = T,
                            saveData = T, 
                            out_algoRunTime = T)

```
  
\begin{verbatim}
Algorithm name: S5.aggregate_allBrands_2010(Market = 'LOS ANGELES', 
                            figurePlot = T,
                            screenPlot = T,
                            saveData = T, 
                            out_algoRunTime = T)  
\end{verbatim}
                            
Algorithm run time: `r difftime(hora[[2]], hora[[1]], units="min") ` minute(s).  
\newpage
  
```{r echo=F, cache=T, message=F, warning=F, fig.height=8, fig.width=9}

par(mfrow= c(1, 2), ps= 8, cex= 0.75, cex.main= 1.25)

hora <- S5.aggregate_allBrands_2010(Market = 'SPOKANE', 
                            figurePlot = T,
                            screenPlot = T,
                            saveData = T, 
                            out_algoRunTime = T)

```
  
\begin{verbatim}
Algorithm name: S5.aggregate_allBrands_2010(Market = 'SPOKANE', 
                            figurePlot = T,
                            screenPlot = T,
                            saveData = T, 
                            out_algoRunTime = T)  
\end{verbatim}
                            
Algorithm run time: `r difftime(hora[[2]], hora[[1]], units="min") ` minute(s).  
\newpage
  
```{r echo=F, cache=T, message=F, warning=F, fig.height=8, fig.width=9}

par(mfrow= c(1, 2), ps= 8, cex= 0.75, cex.main= 1.25)

hora <- S5.aggregate_allBrands_2010(Market = 'SYRACUSE', 
                            figurePlot = T,
                            screenPlot = T,
                            saveData = T, 
                            out_algoRunTime = T)

```
  
\begin{verbatim}
Algorithm name: S5.aggregate_allBrands_2010(Market = 'SYRACUSE', 
                            figurePlot = T,
                            screenPlot = T,
                            saveData = T, 
                            out_algoRunTime = T)  
\end{verbatim}
                            
Algorithm run time: `r difftime(hora[[2]], hora[[1]], units="min") ` minute(s).  
\newpage
  
```{r echo=F, cache=T, message=F, warning=F, fig.height=8, fig.width=9}

par(mfrow= c(1, 2), ps= 8, cex= 0.75, cex.main= 1.25)

hora <- S5.aggregate_allBrands_2010(Market = 'HOUSTON', 
                            figurePlot = T,
                            screenPlot = T,
                            saveData = T, 
                            out_algoRunTime = T)

```
  
\begin{verbatim}
Algorithm name: S5.aggregate_allBrands_2010(Market = 'HOUSTON', 
                            figurePlot = T,
                            screenPlot = T,
                            saveData = T, 
                            out_algoRunTime = T)  
\end{verbatim}
                            
Algorithm run time: `r difftime(hora[[2]], hora[[1]], units="min") ` minute(s).  
\newpage
